Moisture absorption and drying alter nonadditive litter flammability in a mixed conifer forest

### 2020-07-01 ms/Magalhaes_Schwilk_litter_flam_moisture.tex
Finish R4
Final submission after acceptance

\nwords{6330 (main text only), 8000 (abstract, text, captions) }
\ntables{4}
\nfig{3}
\nref{57}

@@

      \item Moisture content is a strong determinant of forest fuel
    flammability, however, little is known about the mechanisms by which
    species-specific litter traits influence litter moisture absorption and
    retention. Characterizing how litter fuels retain moisture through time and
    how fuels from multiple species interact are key steps to adding taxon
    specific information to fire behavior prediction.

@@

\section*{Data and code availability}
All data and code for this project is at
\url{https://github.com/schwilklab/trait-flam}. Checkout git tag ``JoE.1.0''
which contains this manuscript and code needed to create the figures and
tables.

>>>>

\nwords{6330 (main text only), 8000 (abstract, text, captions) }
\ntables{5}
\nfig{3}
\nref{58}

@@

      \item Moisture content is a strong determinant of forest fuel
    flammability. However, little is known about the mechanisms by which
    species-specific litter traits influence litter moisture absorption and
    retention. Characterizing how litter fuels retain moisture through time and
    how fuels from multiple species interact are key steps to adding taxon
    specific information to fire behavior prediction.

@@

\section*{Data and code availability}
All data and code for this project is at \url{http://doi.org/10.5281/zenodo.3905213} and
\url{https://github.com/schwilklab/trait-flam}. Checkout git tag ``JoE.1.0''
which contains this manuscript and code needed to create the figures and
tables.
